\speculake: Hiding Malware in Speculative Execution

### 2018-05-06 paper/implementation.tex

To acheive a balance with speed the number of bits in each instruction is both 
fixed and minimized.  A variable length instruction would require that the prime
and probe stage search the maximum number of bits on each round, and each 
aditional bit doubles the search space that the prime and probe stage must 
traverse.  So every bit shorted effectively doubles the throughput of the 
emulator, and there is effectively no advantage to allowing variable length 
instructions.

@@

Expected performance for a given SPASM binary will vary given multiple factors, 
the most important of which is the prime and probe redundancy. This can be tuned
based on the specific trigger, as it is used to establish confidence that a signal 
has been identified in the indicess returned from the "speculative world". 
Thus accomplishing a task using SPASM generally equates to:

>>>>

To acheive a balance with speed the number of bits in each instruction is both 
fixed and minimized.  A variable length instruction would require that the 
\texttt{Flush+Reload} stage search the maximum number of bits on each round, and each 
aditional bit doubles the search space that the \texttt{Flush+Reload} stage must 
traverse.  So every bit shorted effectively doubles the throughput of the 
emulator, and there is effectively no advantage to allowing variable length 
instructions.

@@

Expected performance for a given SPASM binary will vary given multiple factors, 
the most important of which is the \texttt{Flush+Reload} redundancy. This can be tuned
based on the specific trigger, as it is used to establish confidence that a signal 
has been identified in the indicess returned from the "speculative world". 
Thus accomplishing a task using SPASM generally equates to:
